DPSh: Automated Data-Parallel Processing in the Shell

### 2020-03-21 pldi/draft.tex
Nit

  \item
  \S\ref{ir} presents a dataflow graph model for encoding shell
  scripts, and a set of parallelization transformations that preserve
  the semantics of the sequential program.

>>>>

  \item
  \S\ref{ir} presents a dataflow graph model for encoding shell
  scripts, and a set of safe parallelization transformations that
  preserve the semantics of the sequential program.
